---
title: "Let's start at the very beginning"
subtitle: "A very good place to start"
author: Jen Richmond
institution: R-Ladies Sydney
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "my-theme.css", "my-fonts.css"]
    seal: false 
    lib_dir: libs
    nature:
      highlightStyle: dracula
      highlightLanguage: ["r", "yaml", "markdown"]
      slideNumberFormat: "" 
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
params:
  site_link: "https://do-re-mi.netlify.com/"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
episode_counter <- 0
knitr::opts_chunk$set(
  collapse = TRUE,   
  comment = "#>"
)
```

```{r packages, include=FALSE}
library(countdown)
library(ymlthis)
```


class: title-slide, center, middle

<span class="fa-stack fa-4x">
  <i class="fa fa-circle fa-stack-2x" style="color: #ffffffcc;"></i>
  <strong class="fa-stack-1x" style="color:#e7553c;">`r rmarkdown::metadata$session`</strong>
</span> 

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author` &#183; `r rmarkdown::metadata$institution`

#### [`r params$site_link`](`r params$site_link`)

---
layout: true

<div class="my-footer"><span>`r params$site_link`</span></div>

---

# The Plan

1. Why R?

2. Navigating RStudio

3. Getting your data in

4. Cleaning it up

5. Make a ggplot


--


You will need a laptop and wifi, but we will use RStudio Cloud, so don't worry about installation.

---

## Who are we?

Jen Richmond
- Developmental psychologist UNSW
- Co-founder R-Ladies Sydney
- R beginner :purple heart: 

Charles Gray
- 
- 
- 

Danielle Navarro
- 
- 
- 

---

# Warning

Google is every R user's best friend, even Hadley Wickham. 

https://twitter.com/hadleywickham/status/757919786344984577?lang=en

Today we are really unlikely to know the answers to all your questions, but we can help you google!

https://twitter.com/ResearcHersCode/status/1184483102615191553

---

class: center, middle, inverse
 
# 1. Why R?

Talk to your neighbour, why do you want to learn R?

```{r echo=FALSE}
countdown(minutes = 2, seconds = 00)
```
 
---
  
# Why I R...


### One stop shop 


### Inclusivity 


### Reproducibility


### Community


### Fun!  
 
---

class: center, middle, inverse

# 2.  Navigating RStudio

---

class: center, middle, inverse

# 3. Getting data in

---

class: center, middle, inverse

# 4. Cleaning it up

---

class: center, middle, inverse

# 5. Make a ggplot

---


